Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-05 tex/main.tex
more

\begin{figure}[t]
\normalsize
\centering
\begin{tabular}{l@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r}
  & \multicolumn{2}{c@{\kern0.375em}}{{\bench z3}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4+f}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4+i}}
\\%[-1pt]
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
\\
\midrule
{\bench isa} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
\\
{\bench leon}  & 0 & 2 & 0 & 0 & 0 & {\win 9} & 0 & 0
\\
{\bench isa+m} & 0 & 35 & 0 & 0 & 0 & {\win 153} & 0 & 0
\\
{\bench leon+m}  & 11  & 75 & 6 & 6 & 6 & {\win 169} & 6 & 6
\\[\jot]
Total & \phantom{0}11  & 112 & \phantom{00}6 & \phantom{00}6 & \phantom{00}6 & {\win 331} & \phantom{00}6 & \phantom{00}6
\end{tabular}
\caption{\,Number of ``satisfiable'' responses on benchmarks without and with translation with $\conv$}
\label{fig:sat}
\end{figure}

\begin{figure}[t]
\normalsize
\centering
\begin{tabular}{l@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r}
  & \multicolumn{2}{c@{\kern1.5em}}{{\bench z3}}     & \multicolumn{2}{c@{\kern1.5em}}{{\bench cvc4}}     & \multicolumn{2}{c@{\kern1.5em}}{{\bench cvc4+f}}     & \multicolumn{2}{c@{\kern1.5em}}{{\bench cvc4+i}}
\\%[-1pt]
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
\\
\midrule
{\bench isa} & 14  & 15 & 15  & 15 & 15  & 15 & {\win 61}  & 14
\\
{\bench leon}  & 73  & 78 & 80  & 80 & 80  & 76 & {\win 96}  & 78
\\
{\bench isa+m} & 17  & 18 & 18  & 18 & 18  & 18 & {\win 44}  & 17
\\
{\bench leon+m\phantom{w}}  & 83  & 98 & 103 & 98 & 104 & 95 & {\win 117} & 98
\\[\jot]
Total & 187 & 209 & 216 & 211 & 217 & 204 & {\win 318} & 217
\end{tabular}
\caption{\,Number of ``unsatisfiable'' responses on benchmarks without and with translation with $\conv$}
\label{fig:unsat}
\end{figure}

>>>>

\begin{figure}[t]
\normalsize
\centering
\begin{tabular}{l@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\,\,}}
  & \multicolumn{2}{c@{\kern0.375em}}{{\bench z3}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4+f}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4+i}}
\\%[-1pt]
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
\\
\midrule
{\bench isa} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
\\
{\bench leon}  & 0 & 2 & 0 & 0 & 0 & {\win 9} & 0 & 0
\\
{\bench isa+m} & 0 & 35 & 0 & 0 & 0 & {\win 153} & 0 & 0
\\
{\bench leon+m}  & 11  & 75 & 6 & 6 & 6 & {\win 169} & 6 & 6
\\[\jot]
Total & \phantom{0}11  & 112 & \phantom{00}6 & \phantom{00}6 & \phantom{00}6 & {\win 331} & \phantom{00}6 & \phantom{00}6
\end{tabular}
\caption{\,Number of ``satisfiable'' responses on benchmarks without and with translation with $\conv$}
\label{fig:sat}
\end{figure}

\begin{figure}[t]
\normalsize
\centering
\begin{tabular}{l@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\kern1.5em}r@{\kern0.375em}r@{\,\,}}
  & \multicolumn{2}{c@{\kern0.375em}}{{\bench z3}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4+f}}     & \multicolumn{2}{c@{\kern0.375em}}{{\bench cvc4+i}}
\\%[-1pt]
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
  & \hfill $\varphi$ \hfill & $\conv(\varphi)$\!\!
\\
\midrule
{\bench isa} & 14  & 15 & 15  & 15 & 15  & 15 & {\win 61}  & 14
\\
{\bench leon}  & 73  & 78 & 80  & 80 & 80  & 76 & {\win 96}  & 78
\\
{\bench isa+m} & 17  & 18 & 18  & 18 & 18  & 18 & {\win 44}  & 17
\\
{\bench leon+m}  & 83  & 98 & 103 & 98 & 104 & 95 & {\win 117} & 98
\\[\jot]
Total & 187 & 209 & 216 & 211 & 217 & 204 & {\win 318} & 217
\end{tabular}
\caption{\,Number of ``unsatisfiable'' responses on benchmarks without and with translation with $\conv$}
\label{fig:unsat}
\end{figure}
